Items: German

### 2021-11-03 items_german.Rmd
- set-up of repo

---
title: "Items: English"
output:
  # pdf_document:
  #   latex_engine: xelatex
  #   toc: true
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
---

Here you can find a quick overview of all items that were measured.

@@

"Taken everything together, how satisfied are you currently with your life?"

(0 = extremely unsatisfied, 10 = extremely satisfied)

@@

"In the last week, how often did you feel"

 - a: ... calm and relaxed
 - e: ... happy
 - i: ... full of energy

(never [1]; on some days [2]; several times per week [3]; almost every day [4]; daily [5])

@@

"In the last week, how often did you feel"

 - b: ... lonely
 - c: ... aggravated
 - d: ... so depressed, that nothing could lift you up
 - f: ... very nervous
 - g: ... anxious
 - h: ... glum and sad

(never [1]; on some days [2]; several times per week [3]; almost every day [4]; daily [5])

>>>>

---
title: "Items: German"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
---

Here you can find a quick overview of all items that were measures.

@@

"Alles in allem betrachtet, wie zufrieden sind Sie derzeit mit Ihrem Leben?"

(0 = äußerst unzufrieden, 10 = äußerst zufrieden)

@@

"Wie often waren Sie in der letzten Woche"

 - a: ... ruhig und gelassen
 - e: ... glücklich
 - i: ... voller Energie

@@

"Wie often waren Sie in der letzten Woche"

 - b: ... einsam
 - c: ... ärgerlich
 - d: ... so niedergeschlagen, dass Sie nichts aufheitern konnte
 - f: ... sehr nervös
 - g: ... ängstlich
 - h: ... bedrückt und traurig
